---
title: "Introduction to OntoRetriever"
author: "Zhigang Wang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to HPOretriever}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<style type="text/css">
pre > code.sourceCode {
  white-space: pre-wrap; /* Wraps code */
  word-wrap: break-word; /* Allows long words to break */
  position: relative;
  overflow: auto; /* Adds scrollbars if content overflows */
  font-size: 1.02em; /* Increases the font size */
  background-color: #f8f9fa; /* Sets a lighter background color */
  padding: 10px; /* Adds padding for better readability */
  border-radius: 4px; /* Adds rounded corners to the code block */
}

pre > code.sourceCode > span {
  line-height: 1.5; /* Increases line height for better readability */
  color: inherit; /* Ensures text color is inherited */
  text-decoration: inherit; /* Ensures text decoration is inherited */
}

pre > code.sourceCode > span:empty {
  height: 1.2em;
}

.sourceCode {
  overflow: visible;
}

div.sourceCode {
  margin: 1em 0;
}

pre.sourceCode {
  margin: 0;
  white-space: pre-wrap; /* Ensures code wraps within the box */
  background-color: #f8f9fa; /* Applies a lighter background to pre */
  font-size: 1.02em; /* Matches the font size increase */
}

@media screen {
  div.sourceCode {
    overflow: auto; /* Adds scrollbars for better visibility */
  }
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, echo=T}
reticulate::use_virtualenv(virtualenv='r-reticulate')
library(reticulate)
library(OntoRetriever)
re = retrieve_similar_terms("irritability", onto ="HPO", k = 3)
print(re)

re = retrieve_similar_terms("irritability", onto ="OAE", k = 3)
print(re)

retrieve_similar_terms("tired", onto ="HPO", k = 3)
retrieve_similar_terms("swelling at the injection site", onto ="OAE", k = 3)

re = map_text_to_hpo("The most commonly reported reactions were pain at the injection site and headache.", k = 3)
print(re)

text = "The most commonly reported solicited local and systemic adverse reactions in pregnant
individuals (≥10%) were pain at the injection site (40.6%), headache (31.0%), muscle pain
(26.5%), and nausea (20.0%). (6.1) • The most commonly reported solicited local and systemic
adverse reactions in individuals 60 years of age and older (≥10%) were fatigue (15.5%),
headache (12.8%), pain at the injection site (10.5%), and muscle pain (10.1%). "
re = map_text_to_hpo(ae_text=text, k = 1)
print(re)
re = map_text_to_oae(ae_text=text, k = 1)
print(re)
```

